Numerical error propagation in the HCP structural pre-processing pipelines

### 2018-03-13 paper.tex
Updates following meeting with @ali4006

We reconstruct
the tree of processes starting from the first process created by the pipeline and retrieving its child processes with dependency files in
the next levels from database. \todo{Start here.} The process tree of two subjects has
tested in the same pipeline conditions which are similar, so we
collect such data only for one subject (The term condition refers to
the variation of operating systems on which the data processing takes
place). Furthermore, the process tree is acyclic “with the respect of
this assumption that there is no race conditions between processes to
write on the same file.”
\paragraph{} In the next step, we classify the processes into three categories considering to the obtained process tree 
and the error matrix file. First, processes that read file(s) without error but write different file(s) create error in 
the pipeline. The second group of the processes are those which remove errors in pipeline, read file(s) with error and
 write “nothing or” file(s) without error. Most of the processes are in the third category beyond any fault which
 read and write file(s) without error. The processes in each category may read or write temporary file(s) that implies 
the uncertainty of the process.
\paragraph{} Pipeline is conducted of a bunch of processes sequentially, setting a modification step after classification
 of processes iteratively enables us to control the propagation of errors in the pipeline correctly. In each iteration
 we detect all the processes which are create error in the pipeline and then by fixing those processes artificially, 
we’ll find the other processes in the pipeline that introduce an error. This procedure will be terminated by fixing all the processes. 
To fix the processes that create error, we replace their dependency files with error by the same file copy from the results 
obtained in the other operating system. In this way, we were able to pinpoint the origin of the errors measured in the pipeline.

>>>>

We reconstruct the tree of processes starting from the first process
created by the pipeline and defining its child processes as the ones
that were created through \texttt{clone()} or \texttt{fork()}. We
create a process graph from this tree by adding edges corresponding to
file dependencies between processes. A file dependency is defined
between processes A and B if a file written by A is read by
B. Figure~\ref{fig:graph-example} shows an example of a process graph
constructed at this stage \todo{Build the graph obtained on
  bin/example.sh and add it to the Figure}.
\begin{figure}
%  \includegraphics{brain\_classification}
  \caption{Process graph constructed from an example brain extraction script.}
  \label{fig:graph-example}
\end{figure}

A different process graph may be produced for every subject in every
execution condition. Among our dataset, we identified 4 types of
subjects with different numbers of T1w and T2w images. We verified
that the process graphs were identical for all subjects of the same
type, for all execution conditions. The remainder of the analysis is
done separately for each subject type. \todo{Check that}

Cycles may be present in the process graph in case a file was written
by more than one process.  We remove the cycles in the process graph
by removing file edges between processes A and B when A's process
creation timestamp is posterior to B's or when A=B.

\todo{Start from here}
\paragraph{} In the next step, we classify the processes into three categories considering to the obtained process tree 
and the error matrix file. First, processes that read file(s) without error but write different file(s) create error in 
the pipeline. The second group of the processes are those which remove errors in pipeline, read file(s) with error and
 write “nothing or” file(s) without error. Most of the processes are in the third category beyond any fault which
 read and write file(s) without error. The processes in each category may read or write temporary file(s) that implies 
the uncertainty of the process.
\paragraph{} Pipeline is conducted of a bunch of processes sequentially, setting a modification step after classification
 of processes iteratively enables us to control the propagation of errors in the pipeline correctly. In each iteration
 we detect all the processes which are create error in the pipeline and then by fixing those processes artificially, 
we’ll find the other processes in the pipeline that introduce an error. This procedure will be terminated by fixing all the processes. 
To fix the processes that create error, we replace their dependency files with error by the same file copy from the results 
obtained in the other operating system. In this way, we were able to pinpoint the origin of the errors measured in the pipeline.
